Taking from the rich or giving to the poor: The two faces of support for redistribution

### 2019-04-13 doctoword/manuscript.Rmd
add folder doctoword with manuscript

---
title: "Taking from the rich or giving to the poor: The two faces of support for redistribution"
date: "`r Sys.Date()`"
output:
  workflowr::wflow_html:
    toc: false
---

@@

```{r echo=FALSE, message=FALSE, results='hide'}
data1_raw <- read_sav("data/SDO_2_UV.sav")
data1_raw$sexo[data1_raw$sexo==99] <- NA        #Setting 99 as missing values
data1 <- data1_raw[,c(1,20:70,91:100)] # Selecciono variables de inter?s
data1_redis_full <- data1[complete.cases(data1[,c(26:36)]), ]

@@

library(haven)
data2_raw <- read_sav("data/data2_raw.sav")
data2 <- data2_raw[,c(1,15:74)]

>>>>

---
title: "Taking from the rich or giving to the poor: The two faces of support for redistribution"
date: "`r Sys.Date()`"
output: word_document
---

@@

```{r echo=FALSE, message=FALSE, results='hide'}
data1_raw <- read_sav("../data/SDO_2_UV.sav")
data1_raw$sexo[data1_raw$sexo==99] <- NA        #Setting 99 as missing values
data1 <- data1_raw[,c(1,20:70,91:100)] # Selecciono variables de inter?s
data1_redis_full <- data1[complete.cases(data1[,c(26:36)]), ]

@@

library(haven)
data2_raw <- read_sav("../data/data2_raw.sav")
data2 <- data2_raw[,c(1,15:74)]
